### 2015-09-29 untitled.tex
edited untitled.tex

Theorem 5 in \cite{Raj:suspension1991} provides a very positive result to handle deferrable task systems. That is, if a deferrable task system can be schedulable by using a fixed-priority scheduling policy, the sporadic enforcer algorithm also provides a feasible schedule. However, recall that the deferrable task systems are based on the assumption that a deferrable task $\tau_i$ can defer its entire execution time but not parts of it. If we would like to use this result to handle segmented self-suspending task systems, the first question we have to answer is \emph{"What is the corresponding deferrable task system of a sporadic segmented self-suspending task system?"}. Unfortunately, the report in \cite{Raj:suspension1991} did not provide any explanation about the above question. In this report, we will explain two concepts:
\begin{itemize}
\item First, there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using period enforcer algorithm is not feasible. This shows that the result in Theorem 5 in \cite{Raj:suspension1991} has to be carefully used only based on the schedulability of \emph{deferrable task systems} instead of \emph{self-suspending task systems}.
\item Second, deriving the corresponding deferrable task system of a sporadic segmented self-suspending task system is an open problem to be done in polynomial time. The recent findings by Netlissen et al. \cite{ecrts15nelissen} can be applied, but it takes exponential time.
\end{itemize}

@@

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ (that arrives at time $0$) is executed as if there is no period enforcer. The second job (that releases at time $11$) of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue and scheduled as early as possible.

>>>>

Theorem 5 in \cite{Raj:suspension1991} provides a very positive result to handle deferrable task systems. That is, if a deferrable task system can be schedulable by using a fixed-priority scheduling policy, the perioc enforcer algorithm also provides a feasible schedule. However, recall that the deferrable task systems are based on the assumption that a deferrable task $\tau_i$ can defer its entire execution time but not parts of it. If we would like to use this result to handle segmented self-suspending task systems, the first question we have to answer is \emph{"What is the corresponding deferrable task system of a sporadic segmented self-suspending task system?"}. Unfortunately, the report in \cite{Raj:suspension1991} did not provide any explanation about the above question. In this report, we will explain two concepts:
\begin{itemize}
\item First, there exists (at least) a sporadic segmented self-suspending task system that is schedulable under fixed-priority scheduling without any enforcement, but the corresponding schedule by using the period enforcer algorithm is not feasible. This shows that the result in Theorem 5 in \cite{Raj:suspension1991} has to be carefully used only based on the schedulability of \emph{deferrable task systems} instead of \emph{self-suspending task systems}.
\item Second, deriving the corresponding deferrable task system of a sporadic segmented self-suspending task system is an open problem to be done in polynomial time. The recent findings by Netlissen et al. \cite{ecrts15nelissen} can be applied, but it takes exponential time.
\end{itemize}

@@

Figure \ref{fig:example} is the resulting schedule by using the period enforcer algorithm. The first job of task $\tau_2$ (that arrives at time $0$) is executed as if there is no period enforcement. The second job (that releases at time $11$) of task $\tau_2$ requires some attention to understand how the period enforcer algorithm works. Note that the first computation segment of task $\tau_2$ does not suffer from any deferrable execution (it is postponed due to higher-priority block). Therefore, it is always placed to the ready queue and scheduled as early as possible.
